SIR Model With Testing Flows and Isolation

### 2020-12-02 codes/ali_test_sir.Rmd
panel plot update

```{r packages, message=FALSE}
library(deSolve)
library(ggplot2)
library(tidyr)
library(McMasterPandemic)
library(directlabels)
library(latex2exp)
unpack <- McMasterPandemic::unpack

@@

```{r DFE, message=FALSE}
# DFE; numerical approach
library(rootSolve)
DFE <- function(S,params){
  S_u <- S[1]
  S_n <- S[2]
  I_u <-0
  R_u <-0
  unpack(as.list(params))
  W <- W_S*S_u+W_I*I_u+W_R*R_u
  sigma <- rho*N0/W
  F_S <- sigma*W_S

@@

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
n_out <- 5 ## facets (rows/cols)
n_in <- 41 ## grid N within facets
 # specify the ranges
 beta  <- 0.339  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 eta_c <- seq(0,1, length.out=n_out) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, was 0.011
 W_S <- 1 #choose 0.3 for TTI testing plan and 1 for the random testing.

@@

df2 <- df2 %>% dplyr::mutate(R0_sub = ifelse(eta_w<eta_c, NA, R0))

# df2_fake <- df2 %>% dplyr::select(eta_c,eta_w)
# df2_fake <- unique(df2_fake) %>% dplyr::mutate(flag=ifelse(eta_c<=eta_w,1,0))

@@

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
brks_vec <- seq(0.8,1.05,by=0.05)
p1 <- ggplot(df2,aes(x=omega,y=rho,z=R0_sub))+ theme_bw() +
  xlab(TeX('$\\omega$, Returning test result rate (1/day)')) +
  ylab(TeX('$\\rho$, testing intensity (1/day per capita)')) +
    # theme(panel.spacing=grid::unit(0,"lines")) # initial theme, comment it for TTI testing plot
    theme(panel.spacing=grid::unit(0,"lines"),legend.position = "none") #AG, uncomment for Random Case
# p1_temp <- (p1
#     + geom_contour_filled(breaks=pretty(unique(df2$R0_sub),5),
#                           alpha=0.5) ## breaks=0.2)
#     + geom_contour(breaks=1,alpha=0.5,colour="black")
#     + facet_grid(eta_w~eta_c, labeller=label_special)
#     + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_fill_viridis_d(name=parse(text="R[0]"))
#     + ggtitle(TeX(sprintf("W_S=%.1f, W_I=W_R=1",W_S)))
#     + geom_rect(data=df2,
#                           fill=ifelse(df2$eta_c>df2$eta_w,"white","NA" ),
#                           color= NA,
#                           ymin=-1,
#                           ymax=10,
#                           xmin=-1,
#                           xmax=2)
#     )

p1_temp <- (p1
    + geom_contour_filled(breaks=brks_vec)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(eta_w~eta_c, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"), breaks=brks_vec)
    + ggtitle(TeX(sprintf("W_S=%.1f, W_I=W_R=1",W_S)))
    + geom_rect(data=df2,
                          fill=ifelse(df2$eta_c>df2$eta_w,"white","NA" ),
                          color= NA,
                          ymin=-1,
                          ymax=10,
                          xmin=-1,
                          xmax=2)
    )
p1_temp
# ## hack (By Dr. Ben Bolker) white rectangle to cover grid
#   ggplot() + 
#   scale_x_continuous(name="x") + 
#   scale_y_continuous(name="y") +
#   facet_grid(eta_w~eta_c, labeller=label_special) +
#     geom_rect(data=df2_fake,
#                           fill=ifelse(df2_fake$eta_c>df2_fake$eta_w,"white","black"),
#                           color= NA,
#                           ymin=-1,
#                           ymax=10,
#                           xmin=-1,
#                           xmax=2)

ggsave(p1_temp,filename = "R0contour_random.png" , path="../pix/")
# ggsave(p1_temp,filename = "R0contour_TTI.png" , path="../pix/")

@@

```{r contour_R0_2, message=FALSE,warning=FALSE }
 # specify the ranges
beta  <- 0.339  ## set beta high enough to allow R0>1 in worst case 
rho     <- seq(0,0.01, length.out=n_in)
omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, 
eta_c <- seq(0.001,0.1, length.out=n_out)
s <- seq(1,10,length.out=n_out)

 df11 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,rho=rho,
                    W_S=W_S,W_I=params[["W_I"]],W_R=params[["W_R"]],
                    p_S=params[["p_S"]],p_I=params[["p_I"]],p_R=params[["p_R"]],
                    eta_w=params[["eta_w"]],eta_c=eta_c,s=s)

df22<- data.frame(df11,R0=apply(df11,1,function(params_in)R02(params=params_in)),
                      Fi= apply(df11,1,function(params_in)F_I(params=params_in)),
                       Sn=apply(df11,1,function(params_in)Sn_dfe(params = params_in)))
```

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
p11 <- ggplot(df22,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
p2_temp <- (p11
    + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(s~eta_c, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"),breaks=brks_vec)
    + ggtitle("W[S]=1, W[I]=W[R]=1")
)
p2_temp
## ggsave(p2_temp,filename = "R0contour_random_s.png" , path="../pix/")
ggsave(p2_temp,filename = "R0contour_random_s.pdf" , path="../pix/")
```

@@

```{r  chnages of R0 wrt omega,message=FALSE,warning=FALSE }
R0_omega <- function(params){
  unpack(as.list(params))
         # a <- (eta_w-1)*W_I-(eta_c-1)*p_I*W_I
         a <- ((s-p_I)*eta_c + (p_I-1))*W_I  #involving s
         b <- 2*(eta_w-1)*gamma*W_S
         c <- b*gamma/2

         d <- (-beta*rho)/(gamma*W_S*omega^2*(gamma+omega)^2)*(a*omega^2 + b*omega + c)
         return(d)
}

R0_omega(params)

@@

```{r }
 # specify the ranges
if(F){
beta  <- 0.5  ## set beta 
gamma <- seq(0.1,0.5, length.out=n_out)
p_I <- 0.9

# eta_w <- seq(0,1, length.out=n_out)
eta_c <- seq(0.001,1, length.out=n_out)
s <- seq(1,2,length.out=n_out)

rho <- seq(0,0.01, length.out=n_in)
omega <- seq(0.011,2 , length.out=n_in) #note omega must be > rho, was 0.011

W_S <- 1/100
W_I <- 1/3
W_R <- 1/3

 df3_1 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=gamma,omega=omega,rho=rho,
                    W_S=W_S,W_I=W_I,W_R=W_R,
                    p_S=params[["p_S"]],p_I=p_I,p_R=params[["p_R"]],
                    eta_w=params[["eta_w"]],eta_c=eta_c,s=s)

df3_2 <- data.frame(df3_1,R0=apply(df3_1,1,function(params_in)R02(params=params_in)),
                      R0_omega= apply(df3_1,1,function(params_in)R0_omega(params=params_in))
                       )
}
```

```{r show_contours_3, width=24,height=24,message=FALSE,warning=FALSE}
if(F){
p3 <- ggplot(df3_2,aes(x=omega,y=gamma,z=R0_omega))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
(p3
    + geom_contour_filled(breaks=pretty(unique(df3_2$R0_omega),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=0,alpha=0.5,colour="black")
    + facet_grid(s~eta_c, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="dR[0]"))
)
}
```

>>>>

```{r packages, message=FALSE}
library(deSolve)
library(ggplot2)
library(tidyr)
library(McMasterPandemic)
library(directlabels)
library(latex2exp)
library(rootSolve)
unpack <- McMasterPandemic::unpack

@@

```{r DFE, message=FALSE}
# DFE; numerical approach
DFE <- function(S,params){
  S_u <- S[1]
  S_n <- S[2]
  I_u <-0
  R_u <-0
  unpack(as.list(params))
  W <- W_S*S_u+W_I*I_u+W_R*R_u
  sigma <- rho*N0/W
  F_S <- sigma*W_S

@@

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
n_out <- 5 ## facets (rows/cols)
n_in <- 41 ## grid N within facets
 # specify the ranges
 beta  <- 0.339  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 eta_c <- seq(0,1, length.out=n_out) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, was 0.011
 W_S <- 0.3 #choose 0.3 for TTI testing plan and 1 for the random testing.

@@

df2 <- df2 %>% dplyr::mutate(R0_sub = ifelse(eta_w<eta_c, NA, R0))  
```

@@

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
brks_vec <- seq(0.8,1.05,by=0.05) # Break vector for unifying the legends in Random and TTI testing cases.

p1 <- ggplot(df2,aes(x=omega,y=rho,z=R0_sub))+ theme_bw() +
  xlab(TeX('$\\omega$, Returning test result rate (1/day)')) +
  ylab(TeX('$\\rho$, testing intensity (1/day per capita)')) +
  theme(panel.spacing=grid::unit(0,"lines"),legend.position = c(0.89, 0.73)) # initial theme, comment it for TTI testing plot
  # theme(panel.spacing=grid::unit(0,"lines"),legend.position = "none") #AG, uncomment for Random Case
p1_temp <- (p1
    + geom_contour_filled(breaks=brks_vec)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    # + scale_fill_manual(palette=mycolors(brks_vec),drop=FALSE)
    + facet_grid(eta_w~eta_c, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"),drop=FALSE)
    + ggtitle(TeX(sprintf("W_S=%.1f, W_I=W_R=1",W_S)))
    + geom_rect(data=df2, fill=ifelse(df2$eta_c>df2$eta_w,"grey90","NA" ),
                          color= NA,
                          ymin=-1,
                          ymax=10,
                          xmin=-1,
                          xmax=2)
    )
p1_temp

# ggsave(p1_temp,filename = "R0contour_random.pdf" , path="../pix/")
ggsave(p1_temp,filename = "R0contour_TTI.pdf" , path="../pix/")

@@

```{r contour_R0_2, message=FALSE,warning=FALSE }
# This part is done to carry our simulation when s=eta_c/eta_w is involved. Also to fill the upper triangle panels in the panel plot. 
#  # specify the ranges
# beta  <- 0.339  ## set beta high enough to allow R0>1 in worst case 
# rho     <- seq(0,0.01, length.out=n_in)
# omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, 
# eta_c <- seq(0.001,0.1, length.out=n_out)
# s <- seq(1,10,length.out=n_out) 
# 
#  df11 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,rho=rho,
#                     W_S=W_S,W_I=params[["W_I"]],W_R=params[["W_R"]],
#                     p_S=params[["p_S"]],p_I=params[["p_I"]],p_R=params[["p_R"]],
#                     eta_w=params[["eta_w"]],eta_c=eta_c,s=s)
# 
# df22<- data.frame(df11,R0=apply(df11,1,function(params_in)R02(params=params_in)),
#                       Fi= apply(df11,1,function(params_in)F_I(params=params_in)),
#                        Sn=apply(df11,1,function(params_in)Sn_dfe(params = params_in)))

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
# p11 <- ggplot(df22,aes(x=omega,y=rho,z=R0))+ theme_bw() +
#     theme(panel.spacing=grid::unit(0,"lines"))
# p2_temp <- (p11
#     + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
#                           alpha=0.5) ## breaks=0.2)
#     + geom_contour(breaks=1,alpha=0.5,colour="black")
#     + facet_grid(s~eta_c, labeller=label_special)
#     + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_fill_viridis_d(name=parse(text="R[0]"),breaks=brks_vec)
#     + ggtitle("W[S]=1, W[I]=W[R]=1")
# )
# p2_temp
# ## ggsave(p2_temp,filename = "R0contour_random_s.png" , path="../pix/")
# # ggsave(p2_temp,filename = "R0contour_random_s.pdf" , path="../pix/")
```

@@

```{r  chnages of R0 wrt omega,message=FALSE,warning=FALSE }
# R0_omega <- function(params){
#   unpack(as.list(params))
#          # a <- (eta_w-1)*W_I-(eta_c-1)*p_I*W_I
#          a <- ((s-p_I)*eta_c + (p_I-1))*W_I  #involving s
#          b <- 2*(eta_w-1)*gamma*W_S
#          c <- b*gamma/2
#          
#          d <- (-beta*rho)/(gamma*W_S*omega^2*(gamma+omega)^2)*(a*omega^2 + b*omega + c)
#          return(d)
# }
# 
# R0_omega(params)

@@

```{r }
 # specify the ranges
# if(F){
# beta  <- 0.5  ## set beta 
# gamma <- seq(0.1,0.5, length.out=n_out)
# p_I <- 0.9
# 
# # eta_w <- seq(0,1, length.out=n_out)
# eta_c <- seq(0.001,1, length.out=n_out)
# s <- seq(1,2,length.out=n_out)
# 
# rho <- seq(0,0.01, length.out=n_in)
# omega <- seq(0.011,2 , length.out=n_in) #note omega must be > rho, was 0.011
# 
# W_S <- 1/100
# W_I <- 1/3
# W_R <- 1/3
# 
#  df3_1 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=gamma,omega=omega,rho=rho,
#                     W_S=W_S,W_I=W_I,W_R=W_R,
#                     p_S=params[["p_S"]],p_I=p_I,p_R=params[["p_R"]],
#                     eta_w=params[["eta_w"]],eta_c=eta_c,s=s)
# 
# df3_2 <- data.frame(df3_1,R0=apply(df3_1,1,function(params_in)R02(params=params_in)),
#                       R0_omega= apply(df3_1,1,function(params_in)R0_omega(params=params_in))
#                        )
# }
```

```{r show_contours_3, width=24,height=24,message=FALSE,warning=FALSE}
# if(F){
# p3 <- ggplot(df3_2,aes(x=omega,y=gamma,z=R0_omega))+ theme_bw() +
#     theme(panel.spacing=grid::unit(0,"lines"))
# (p3
#     + geom_contour_filled(breaks=pretty(unique(df3_2$R0_omega),5),
#                           alpha=0.5) ## breaks=0.2)
#     + geom_contour(breaks=0,alpha=0.5,colour="black")
#     + facet_grid(s~eta_c, labeller=label_special)
#     + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_fill_viridis_d(name=parse(text="dR[0]"))
# )
# }
```
